A weakly structured stem for human origins in Africa

### 2022-03-04 paper.tex
add Tim's section to conclusion

\usepackage{fullpage}
\usepackage{listings}
\usepackage{url}
\usepackage{authblk}
\usepackage{graphicx}
\usepackage{color}
\usepackage{booktabs}

\lstset{language=Python}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics{figures/fig1.pdf}
    \caption{
        \textbf{Genetic diversity across Africa.}
        (A) Select populations from the 1000 Genomes and African Diversity Reference Panels
        illustrate diversity from western, eastern and southern Africa.
        We chose representatives from each region to build parameterized models,
        including the newly-sequenced Nama from South Africa, Mende
        from Sierre Leone, Gumuz, Oromo and Amhara from Ethiopia, and the
        British and Vindija Neanderthal individual.
        (B, C) PCA highlights the range of genetic divergence anchored 
        by western Africans, Nama, Gumuz and the British.
        Percentages show variance explained by each principal component.
        (D) \texttt{ADMIXTURE} illustrates signatures of recent gene flow in Africa
        which reflect colonial-period migration into the Nama,
        Back-to-Africa gene flow among some Ethiopians, and Khoe-San admixture in the Zulu.
    }
    \label{fig:1}
\end{figure}

@@

Multiple studies have shown a correspondence between phenotypic
differentiation, usually assessed with measurements of the cranium, and genetic
differentiation among human populations and between humans and Neanderthals
\citep{Relethford1994-mh,Weaver2008-ho,Von_Cramon-Taubadel2009-zb}. If we
assume that this correspondence also holds for early human ancestral
populations in Africa, the weakly-structured-stem model would predict that the
fossils deriving from each of the two stems should be morphologically quite
similar (supplementary text \sgcomment{X}), even if
they are from different parts of Africa, with differences across stems closer
to those across contemporary human populations than to human-Neanderthal
differences. Identifying the morphological signature of ancient
structure in the fossil record will thus require careful analysis of many broadly
similar remains. Morphologically distinct
crania such as \sgcomment{XX} and \sgcomment{YY} are unlikely representatives of branches that
contributed appreciably to modern human ancestries.

>>>>

\usepackage[margin=1in]{geometry}
%\usepackage{showframe}
\usepackage{url}
\usepackage{authblk}
\usepackage{graphicx}
\usepackage{color}
\usepackage{booktabs}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics{figures/fig1.pdf}
    \caption[width=\textwidth]{
        \textbf{Genetic diversity across Africa.}
        (A) Select populations from the 1000 Genomes and African Diversity Reference Panels
        illustrate diversity from western, eastern and southern Africa.
        We chose representatives from each region to build parameterized models,
        including the newly-sequenced Nama from South Africa, Mende
        from Sierre Leone, Gumuz, Oromo and Amhara from Ethiopia, and the
        British and Vindija Neanderthal individual.
        (B, C) PCA highlights the range of genetic divergence anchored 
        by western Africans, Nama, Gumuz and the British.
        Percentages show variance explained by each principal component.
        (D) \texttt{ADMIXTURE} illustrates signatures of recent gene flow in Africa
        which reflect colonial-period migration into the Nama,
        Back-to-Africa gene flow among some Ethiopians, and Khoe-San admixture in the Zulu.
    }
    \label{fig:1}
\end{figure}

@@

Multiple studies have shown a correspondence between phenotypic
differentiation, usually assessed with measurements of the cranium, and genetic
differentiation among human populations and between humans and Neanderthals
\citep{Relethford1994-mh,Weaver2008-ho,Von_Cramon-Taubadel2009-zb}. The fossil
record of Africa is sparse during the time period of the stems, but of the
available fossils, some are very similar to present-day humans (e.g., from Omo
Kibish, Ethiopia), others are similar in some features but not others (e.g.,
from Jebel Irhoud, Morocco), and others are very different (e.g., from
Dinaledi, South Africa) in morphology. If, as our model predicts, the
morphological differences between the stems were comparable to those among
present-day human populations, the most divergent fossils are unlikely to
represent the branches that contributed appreciably to present-day human
ancestries.

%If we
%assume that this correspondence also holds for early human ancestral
%populations in Africa, the weakly-structured-stem model would predict that the
%fossils deriving from each of the two stems should be morphologically quite
%similar (supplementary text \sgcomment{X}), even if
%they are from different parts of Africa, with differences across stems closer
%to those across contemporary human populations than to human-Neanderthal
%differences. Identifying the morphological signature of ancient
%structure in the fossil record will thus require careful analysis of many broadly
%similar remains. Morphologically distinct
%crania such as \sgcomment{XX} and \sgcomment{YY} are unlikely representatives of branches that
%contributed appreciably to modern human ancestries.
